Boundary Labeling for annotated documents

### 2018-01-12 LaTeX/Paper.tex
Paper: Added FromTextToGraph.png (needs further work) and included references to it. Program: No changes.

These properties were modelled by creating a rectangle around each word that no leaders may pass through. If this is done for all words in a paragraph, the remaining available space for routing resembles a grid of perfectly parallel streets. \change{NOTE: Insert example image for this and graph.} Since the layout encourages the usage of P- and O-segments, we decided to represent the possible routes by creating a graph which has its vertices located whenever multiple directions are available - in between lines, above or below whitespace characters. The graph's edges represent the different possible segments of a leader and connect each vertex with the closest vertices directly above, below or to the sides, given that no text is blocking the connection. \change{The resulting graph looks similar to the one in Fig.~<TODO>}

>>>>

\begin{figure}
 \captionsetup{justification=centering, margin=0.75cm}
 \centering
  \includegraphics[scale=0.85]{FromTextToGraph.png}
  \caption{Visualization of the space reserved for the text, and the resulting graph.}
 \label{fig:ttg}
\end{figure}

These properties were modelled by creating a rectangle around each word that no leaders may pass through. If this is done for all words in a paragraph, the remaining available space for routing resembles a grid, like in Fig.\ref{fig:ttg}a.

Since the layout encourages the usage of P- and O-segments, we decided to represent the possible routes by creating a graph which has its vertices located whenever multiple directions are available - in between lines, above or below whitespace characters. The graph's edges represent the different possible segments of a leader and connect each vertex with the closest vertices directly above, below or to the sides, given that no text is blocking the connection. The resulting graph looks similar to the one in Fig.~\ref{fig:ttg}b.
